Cards model analysis

### 2020-03-30 cards_model_analysis.Rmd
Metaclass lesion

---
title: "Cards persistent analysis"
author: "Andrew Lampinen"
output: html_document
---

@@

```{r}
parent_dir = "./presentable_results"
subdirs = c("exact_eval")
language_subdirs = c("exact_eval/language", "exact_eval/tcnh_more_complex/language")

@@

selected_meta_true_d_3 = meta_true_d %>%
  filter(epoch > 5000, epoch < 50000) %>%
  filter(meta_task=="toggle_losers") %>%
  mutate(source_type=case_when(
    base_task_toe == "example_is_train" ~ "train",
    source == "game_straight_flush_l_0_bv_0_sr_0" ~ "eval_target",
    T ~ "eval_other")) %>%
  group_by(run_type, run, epoch, source_type) %>%
  summarize(mean_loss=mean(loss)) %>%
  ungroup() %>%
  spread(source_type, mean_loss) %>%
  left_join(source_task_loss_d) %>%
  mutate(source_loss_and_other = source_task_base_loss + eval_other) %>%
  group_by(run_type, run) %>%
  filter(source_loss_and_other == max(source_loss_and_other))
selected_meta_true_d_3 %>%
  arrange(desc(source_loss_and_other))
```

@@

```{r}
diss_figure_data = bind_rows(
  selected_lang_d %>%
    filter(run_type == "exact_eval/language") %>%
    ungroup() %>%
    select(run, source, eval_target) %>%
    mutate(result_type = "Language baseline"),
  selected_lang_d %>%
    filter(run_type == "exact_eval/tcnh_more_complex/language") %>%
    ungroup() %>%
    select(run, source, eval_target) %>%
    mutate(result_type = "Language baseline\n(task-conditioned)"),
  selected_meta_true_d_3 %>%
    ungroup() %>%
    rename(source=source_task_base_loss) %>%
    select(run, source, eval_target) %>%
    mutate(result_type = "HoMM")) %>%
  gather(task, expected_reward, source, eval_target)
```

>>>>

---
title: "Cards model analysis"
author: "Andrew Lampinen"
output: html_document
---

@@

```{r}
parent_dir = "./presentable_results"
subdirs = c("exact_eval", "exact_eval/metaclass_lesion")
language_subdirs = c("exact_eval/language", "exact_eval/tcnh_more_complex/language")

@@

selected_meta_true_d_3 = meta_true_d %>%
  filter(epoch > 5000, epoch < 50000) %>%
  filter(meta_task=="toggle_losers") %>%
  mutate(source_type=case_when(
    base_task_toe == "example_is_train" ~ "train",
    source == "game_straight_flush_l_0_bv_0_sr_0" ~ "eval_target",
    T ~ "eval_other")) %>%
  group_by(run_type, run, epoch, source_type) %>%
  summarize(mean_loss=mean(loss)) %>%
  ungroup() %>%
  spread(source_type, mean_loss) %>%
  left_join(source_task_loss_d) %>%
  mutate(source_loss_and_other = source_task_base_loss + eval_other) %>%
  group_by(run_type, run) %>%
  filter(source_loss_and_other == max(source_loss_and_other)) %>%
  slice(1) # take first where multiple minima
selected_meta_true_d_3 %>%
  arrange(desc(source_loss_and_other))
```

@@

```{r}
diss_figure_data = bind_rows(
  selected_lang_d %>%
    filter(run_type == "exact_eval/language") %>%
    ungroup() %>%
    select(run, source, eval_target) %>%
    mutate(result_type = "Language baseline"),
  selected_lang_d %>%
    filter(run_type == "exact_eval/tcnh_more_complex/language") %>%
    ungroup() %>%
    select(run, source, eval_target) %>%
    mutate(result_type = "Language baseline\n(task-conditioned)"),
  selected_meta_true_d_3 %>%
    ungroup() %>%
    filter(run_type == "exact_eval/metaclass_lesion") %>%
    rename(source=source_task_base_loss) %>%
    select(run, source, eval_target) %>%
    mutate(result_type = "Meta-class lesion"),
  selected_meta_true_d_3 %>%
    ungroup() %>%
    filter(run_type == "exact_eval") %>%
    rename(source=source_task_base_loss) %>%
    select(run, source, eval_target) %>%
    mutate(result_type = "HoMM")) %>%
  gather(task, expected_reward, source, eval_target)
```
